Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-11-25 LaTeX_paper/paper.tex
improve  "out implementation" section

The next step following the general structure~\cref{document:splitter}
is to split a piece into
his 4 sides, this could be done with the following steps:

@@

\begin{figure}
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/original_piece.jpeg}
    \caption{Original binary mask of a piece.}
    \label{fig:s_s_og}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/remove_holes_convex_hull.png}
    \caption{Convex Hull of a piece.}
    \label{fig:s_s_ch}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/remove_holes_filler_areas.png}
    \caption{Difference:~\cref{fig:s_s_ch} \textminus~\cref{fig:s_s_og}.}
    \label{fig:fig:s_s_og_minus_ch}
  \end{subfigure}
  \vspace{1cm}
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/piece_with_no_hole.png}
    \caption{Piece~\cref{fig:s_s_og} with holes removed.}
    \label{fig:s_s_no_holes}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/remove_knobs_erosion.png}
    \caption{Mask~\cref{fig:s_s_no_holes} eroded.}
    \label{fig:s_s_erosion}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/remove_knobs_expansion.png}
    \caption{Mask~\cref{fig:s_s_erosion} dilated.}
    \label{fig:s_s_dilatation}
  \end{subfigure}
  \vspace{1cm}
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/remove_knobs_knob_pixels.png}
    \caption{Difference:~\cref{fig:s_s_no_holes} \textminus~\cref{fig:s_s_erosion}.}
    \label{fig:s_s_no_holes_minus_expansion}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/piece_with_no_knobs.png}
    \caption{Piece~\cref{fig:s_s_no_holes} with knobs removed.}
    \label{fig:s_s_no_knobs}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/find_corners_min_enclosing_rectangle.png}
    \caption{Min enclosing rectangle of~\cref{fig:s_s_no_knobs}.}
    \label{fig:s_s_min_enc_rec}
  \end{subfigure}
\end{figure}
\clearpage
\begin{figure}\ContinuedFloat
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/find_corners_min_enclosing_triangle.png}
    \caption{Min enclosing triangle of the bottom right corner of~\cref{fig:s_s_no_knobs}.}
    \label{fig:s_s_min_enc_triangle}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/corners_found.png}
    \caption{The corners of the piece~\cref{fig:s_s_og}.}
    \label{fig:s_s_corners_found}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/piece_side.png}
    \caption{One of the sides of the piece~\cref{fig:s_s_og}.}
    \label{fig:s_s_a_piece_side}
  \end{subfigure}

@@

\subsection{Our Comparator}\label{document:my_comparator}
The last step in the setup, is to compare the sides that have been
generated before.
In order to generate a compatibility shore,
the program compute the following steps:

>>>>

The next step following the general structure~\cref{document:splitter}
is to split a piece into
his 4 sides, this can be done with the following steps:

@@

\begin{figure}
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/original_piece.jpeg}
    \caption{Original binary mask of a piece.}
    \label{fig:s_s_og}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/remove_holes_convex_hull.png}
    \caption{Convex Hull of a piece.}
    \label{fig:s_s_ch}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/remove_holes_filler_areas.png}
    \caption{Difference:~\cref{fig:s_s_ch} \textminus~\cref{fig:s_s_og}.}
    \label{fig:fig:s_s_og_minus_ch}
  \end{subfigure}
  \vspace{1cm}
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/piece_with_no_hole.png}
    \caption{Piece~\cref{fig:s_s_og} with holes removed.}
    \label{fig:s_s_no_holes}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/remove_knobs_erosion.png}
    \caption{Mask~\cref{fig:s_s_no_holes} eroded.}
    \label{fig:s_s_erosion}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/remove_knobs_expansion.png}
    \caption{Mask~\cref{fig:s_s_erosion} dilated.}
    \label{fig:s_s_dilatation}
  \end{subfigure}
  \vspace{1cm}
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/remove_knobs_knob_pixels.png}
    \caption{Difference:~\cref{fig:s_s_no_holes} \textminus~\cref{fig:s_s_dilatation}.}
    \label{fig:s_s_no_holes_minus_expansion}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/piece_with_no_knobs.png}
    \caption{Piece~\cref{fig:s_s_no_holes} with knobs removed.}
    \label{fig:s_s_no_knobs}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/find_corners_min_enclosing_rectangle.png}
    \caption{Min enclosing rectangle of~\cref{fig:s_s_no_knobs}.}
    \label{fig:s_s_min_enc_rec}
  \end{subfigure}
\end{figure}
\clearpage
\begin{figure}\ContinuedFloat
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/find_corners_min_enclosing_triangle.png}
    \caption{Min enclosing triangle of the bottom right corner of~\cref{fig:s_s_no_knobs}.}
    \label{fig:s_s_min_enc_triangle}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/corners_found.png}
    \caption{The corners of the piece~\cref{fig:s_s_og}.}
    \label{fig:s_s_corners_found}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.3\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/piece_side.png}
    \caption{One of the sides of the piece~\cref{fig:s_s_og}.}
    \label{fig:s_s_a_piece_side}
  \end{subfigure}

@@

\subsection{Our Comparator}\label{document:my_comparator}
The next step is to compare the sides that have been
generated before, in order to generate
a compatibility shore.
To achieve this, the program employs
the following steps:
